\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Cole,
    middleinitial=H,
    lastname=Rottenberg,
    email=cole.rottenberg@gmail.com,
    phone=407-961-0600,
    linkedin=colerottenberg,
    github=colerotteberg,
    city=Orlando,
    state=Florida,
]

\vspace{0.25in}
\today
\vspace{0.15in}

Dear Hiring Manager,

I am writing to express my keen interest in the Research Intern position at Voloridge Investment Management. As a dedicated Computer Engineering student at the University of Florida with a passion for systematic trading and a background in software engineering, I am excited about the opportunity to contribute to your team and further develop my skills in a dynamic and innovative environment.

During my academic journey, I have honed a strong foundation in data
science and machine learning, complementing my software engineering
skills.
This unique blend of knowledge has been instrumental in my role as an
Assistant Portfolio Manager with AlgoGators, a university-affiliated
systematic trading club.
Managing divergent strategies within our sizable portfolio, which
involves trading over \$500,000, I have not only developed a keen eye for
market trends but also a deep understanding of applying theoretical
concepts in a practical, results-oriented setting.
My experience in embedding these strategies into a system that analyzes daily positions has been both challenging and rewarding, underscoring my passion for the field.

Previously, I expanded my technical expertise through a Software
Engineering internship focusing on embedded systems.
This experience further solidified my programming skills and my ability to thrive in fast-paced, technologically driven environments.

What draws me to Voloridge Investment Management is the prospect of
engaging in experimental research with the extensive datasets at your
disposal.
The opportunity to delve into such rich resources and contribute to
groundbreaking financial strategies is a challenge I am eager to
undertake.
I am particularly interested in how my background in systematic trading and data-driven decision-making can be applied to Voloridge's innovative approaches in the financial market.

I am excited about the prospect of joining Voloridge and contributing my skills and enthusiasm to your team. I am eager to bring my blend of academic knowledge and practical experience to an environment that values innovation and excellence. Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to the ongoing success of Voloridge Investment Management.
Thank you for taking the time to review my application. I look forward
to hopefully meeting with you in the future to further discuss my
qualifications for a position as a Research Intern at Voloridge
this upcoming summer. If you have any questions, please feel free to
email me at \href{mailto:cole.rottenberg@gmail.com}{cole.rottenberg@gmail.com} or
call me at \href{tel:+1-407-961-0600}{407-961-0600}.

Sincerely,

\vspace{.15in}

Cole Rottenberg

\end{document}